---
title: "Process_Results"
author: "Catherine Wenger"
date: "2025-02-19"
output: html_document
---

###############################################################################
# Evaluating the Impact and Cost-Effectiveness of Typhoid Conjugate Vaccine 
#   Schedules across Diverse Settings: a Multi-Model Comparison
# 
# Code to generate cases and doses from the transmission dynamic model output
#
# Created: Catherine Wenger Jan 2025
###############################################################################

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyr)
library(ggplot2)
library(dplyr)
library(ppcor)
library(reshape)
library(reshape2)
library(tidyverse)
## load functions that will be used to process the epidemiological data
source(here("~/Process_TDM_output","post_count_doses_by_year.R"))
source(here("~/Process_TDM_output","post_cases_per_year.R"))
## create directories for each scenario combination (9moW, 9moWO, 15moW, 15moWO)
dir.create("~/Process_TDM_output/Output/9moW", recursive = TRUE, showWarnings = FALSE)
dir.create("~/Process_TDM_output/Output/9moWO", recursive = TRUE, showWarnings = FALSE)
dir.create("~/Process_TDM_output/Output/15moW", recursive = TRUE, showWarnings = FALSE)
dir.create("~/Process_TDM_output/Output/15moWO", recursive = TRUE, showWarnings = FALSE)
```

##Vaccination Strategies:::
#   A - No vaccination
#   B - Routine @ 9mo without catch-up
#   C - Routine @ 9mo with catch-up
#   D - Routine @ 15mo without catch-up
#   E - Routine @ 15mo with catch-up
#   F - Routine @ 2yrs without catch-up
#   G - Routine @ 2yrs with catch-up
#   H - Routine @ 5yrs without catch-up
#   I - Routine @ 5yrs with catch-up
#   J - Routine @ 9mo without catch-up + 5yrs Booster
#   K - Routine @ 9mo with catch-up + 5yrs Booster
#   L - Routine @ 15mo without catch-up + 5yrs Booster
#   M - Routine @ 15mo with catch-up + 5yrs Booster
#   N - Routine @ 9mo without catch-up + 5 & 10yrs Booster
#   O - Routine @ 9mo with catch-up + 5 & 10yrs Booster
#   P - Routine @ 15mo without catch-up + 5 & 10yrs Booster
#   Q - Routine @ 15mo with catch-up + 5 & 10yrs Booster

## arch = incidence archetype
## scen = waning scenario
## filepath - indicates the folders in which the 9mo vs 15mo earliest vaccination 
##            and with and without catch-up campaign are stored separately

### MEDIUM INCIDENCE
## Slow waning | 9 mo with catch-up campaign 
```{r}
arch = c("Medium")
scen = c("Slow")
filepath = c("9moW")
## Load all of the vaccine strategies to be analyzed in this scenario
load("~/Transmission_dynamic_model/Output/Scenario_MediumA_Slow_Results.Rdata")
Scenario_MediumA_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumC_Slow_Results.Rdata")
Scenario_MediumC_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumG_Slow_Results.Rdata")
Scenario_MediumG_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumI_Slow_Results.Rdata")
Scenario_MediumI_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumK_Slow_Results.Rdata")
Scenario_MediumK_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumO_Slow_Results.Rdata")
Scenario_MediumO_Slow_Results <- results
results = c(Scenario_MediumA_Slow_Results,
            Scenario_MediumC_Slow_Results,
            Scenario_MediumG_Slow_Results,
            Scenario_MediumI_Slow_Results,
            Scenario_MediumK_Slow_Results,
            Scenario_MediumO_Slow_Results)
list_process = c("Scenario_MediumA_Slow_Results",
                 "Scenario_MediumC_Slow_Results",
                 "Scenario_MediumG_Slow_Results",
                 "Scenario_MediumI_Slow_Results",
                 "Scenario_MediumK_Slow_Results",
                 "Scenario_MediumO_Slow_Results")
## process data for cost-effectiveness analysis
count_doses_by_year(results,list_process,arch,scen,filepath)
cases_per_year(results,list_process,arch,scen,filepath)
```
## Slow waning | 9 mo without catch-up campaign 
```{r}
arch = c("Medium")
scen = c("Slow")
filepath = c("9moWO")
## Load all of the vaccine strategies to be analyzed in this scenario
load("~/Transmission_dynamic_model/Output/Scenario_MediumA_Slow_Results.Rdata")
Scenario_MediumA_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumB_Slow_Results.Rdata")
Scenario_MediumB_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumF_Slow_Results.Rdata")
Scenario_MediumF_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumH_Slow_Results.Rdata")
Scenario_MediumH_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumJ_Slow_Results.Rdata")
Scenario_MediumJ_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumN_Slow_Results.Rdata")
Scenario_MediumN_Slow_Results <- results
results = c(Scenario_MediumA_Slow_Results,
            Scenario_MediumB_Slow_Results,
            Scenario_MediumF_Slow_Results,
            Scenario_MediumH_Slow_Results,
            Scenario_MediumJ_Slow_Results,
            Scenario_MediumN_Slow_Results)
list_process = c("Scenario_MediumA_Slow_Results",
                 "Scenario_MediumB_Slow_Results",
                 "Scenario_MediumF_Slow_Results",
                 "Scenario_MediumH_Slow_Results",
                 "Scenario_MediumJ_Slow_Results",
                 "Scenario_MediumN_Slow_Results")
## process data for cost-effectiveness analysis
count_doses_by_year(results,list_process,arch,scen,filepath)
cases_per_year(results,list_process,arch,scen,filepath)
```
## Fast waning | 9 mo with catch-up campaign 
```{r}
arch = c("Medium")
scen = c("Fast")
filepath = c("9moW")
## Load all of the vaccine strategies to be analyzed in this scenario
load("~/Transmission_dynamic_model/Output/Scenario_MediumA_Fast_Results.Rdata")
Scenario_MediumA_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumC_Fast_Results.Rdata")
Scenario_MediumC_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumG_Fast_Results.Rdata")
Scenario_MediumG_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumI_Fast_Results.Rdata")
Scenario_MediumI_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumK_Fast_Results.Rdata")
Scenario_MediumK_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumO_Fast_Results.Rdata")
Scenario_MediumO_Fast_Results <- results
results = c(Scenario_MediumA_Fast_Results,
            Scenario_MediumC_Fast_Results,
            Scenario_MediumG_Fast_Results,
            Scenario_MediumI_Fast_Results,
            Scenario_MediumK_Fast_Results,
            Scenario_MediumO_Fast_Results)
list_process = c("Scenario_MediumA_Fast_Results",
                 "Scenario_MediumC_Fast_Results",
                 "Scenario_MediumG_Fast_Results",
                 "Scenario_MediumI_Fast_Results",
                 "Scenario_MediumK_Fast_Results",
                 "Scenario_MediumO_Fast_Results")
## process data for cost-effectiveness analysis
count_doses_by_year(results,list_process,arch,scen,filepath)
cases_per_year(results,list_process,arch,scen,filepath)
```
## Fast waning | 9 mo without catch-up campaign 
```{r}
arch = c("Medium")
scen = c("Fast")
filepath = c("9moWO")
## Load all of the vaccine strategies to be analyzed in this scenario
load("~/Transmission_dynamic_model/Output/Scenario_MediumA_Fast_Results.Rdata")
Scenario_MediumA_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumB_Fast_Results.Rdata")
Scenario_MediumB_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumF_Fast_Results.Rdata")
Scenario_MediumF_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumH_Fast_Results.Rdata")
Scenario_MediumH_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumJ_Fast_Results.Rdata")
Scenario_MediumJ_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumN_Fast_Results.Rdata")
Scenario_MediumN_Fast_Results <- results
results = c(Scenario_MediumA_Fast_Results,
            Scenario_MediumB_Fast_Results,
            Scenario_MediumF_Fast_Results,
            Scenario_MediumH_Fast_Results,
            Scenario_MediumJ_Fast_Results,
            Scenario_MediumN_Fast_Results)
list_process = c("Scenario_MediumA_Fast_Results",
                 "Scenario_MediumB_Fast_Results",
                 "Scenario_MediumF_Fast_Results",
                 "Scenario_MediumH_Fast_Results",
                 "Scenario_MediumJ_Fast_Results",
                 "Scenario_MediumN_Fast_Results")
## process data for cost-effectiveness analysis
count_doses_by_year(results,list_process,arch,scen,filepath)
cases_per_year(results,list_process,arch,scen,filepath)
```
## Slow waning | 15 mo with catch-up campaign 
```{r}
arch = c("Medium")
scen = c("Slow")
filepath = c("15moW")
## Load all of the vaccine strategies to be analyzed in this scenario
load("~/Transmission_dynamic_model/Output/Scenario_MediumA_Slow_Results.Rdata")
Scenario_MediumA_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumE_Slow_Results.Rdata")
Scenario_MediumE_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumG_Slow_Results.Rdata")
Scenario_MediumG_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumI_Slow_Results.Rdata")
Scenario_MediumI_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumM_Slow_Results.Rdata")
Scenario_MediumM_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumQ_Slow_Results.Rdata")
Scenario_MediumQ_Slow_Results <- results
results = c(Scenario_MediumA_Slow_Results,
            Scenario_MediumE_Slow_Results,
            Scenario_MediumG_Slow_Results,
            Scenario_MediumI_Slow_Results,
            Scenario_MediumM_Slow_Results,
            Scenario_MediumQ_Slow_Results)
list_process = c("Scenario_MediumA_Slow_Results",
                 "Scenario_MediumE_Slow_Results",
                 "Scenario_MediumG_Slow_Results",
                 "Scenario_MediumI_Slow_Results",
                 "Scenario_MediumM_Slow_Results",
                 "Scenario_MediumQ_Slow_Results")
## process data for cost-effectiveness analysis
count_doses_by_year(results,list_process,arch,scen,filepath)
cases_per_year(results,list_process,arch,scen,filepath)
```
## Slow waning | 15 mo without catch-up campaign 
```{r}
arch = c("Medium")
scen = c("Slow")
filepath = c("15moWO")
## Load all of the vaccine strategies to be analyzed in this scenario
load("~/Transmission_dynamic_model/Output/Scenario_MediumA_Slow_Results.Rdata")
Scenario_MediumA_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumD_Slow_Results.Rdata")
Scenario_MediumD_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumF_Slow_Results.Rdata")
Scenario_MediumF_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumH_Slow_Results.Rdata")
Scenario_MediumH_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumL_Slow_Results.Rdata")
Scenario_MediumL_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumP_Slow_Results.Rdata")
Scenario_MediumP_Slow_Results <- results
results = c(Scenario_MediumA_Slow_Results,
            Scenario_MediumD_Slow_Results,
            Scenario_MediumF_Slow_Results,
            Scenario_MediumH_Slow_Results,
            Scenario_MediumL_Slow_Results,
            Scenario_MediumP_Slow_Results)
list_process = c("Scenario_MediumA_Slow_Results",
                 "Scenario_MediumD_Slow_Results",
                 "Scenario_MediumF_Slow_Results",
                 "Scenario_MediumH_Slow_Results",
                 "Scenario_MediumL_Slow_Results",
                 "Scenario_MediumP_Slow_Results")
## process data for cost-effectiveness analysis
count_doses_by_year(results,list_process,arch,scen,filepath)
cases_per_year(results,list_process,arch,scen,filepath)
```
## Fast waning | 15 mo with catch-up campaign 
```{r}
arch = c("Medium")
scen = c("Fast")
filepath = c("15moW")
## Load all of the vaccine strategies to be analyzed in this scenario
load("~/Transmission_dynamic_model/Output/Scenario_MediumA_Fast_Results.Rdata")
Scenario_MediumA_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumE_Fast_Results.Rdata")
Scenario_MediumE_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumG_Fast_Results.Rdata")
Scenario_MediumG_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumI_Fast_Results.Rdata")
Scenario_MediumI_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumM_Fast_Results.Rdata")
Scenario_MediumM_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumQ_Fast_Results.Rdata")
Scenario_MediumQ_Fast_Results <- results
results = c(Scenario_MediumA_Fast_Results,
            Scenario_MediumE_Fast_Results,
            Scenario_MediumG_Fast_Results,
            Scenario_MediumI_Fast_Results,
            Scenario_MediumM_Fast_Results,
            Scenario_MediumQ_Fast_Results)
list_process = c("Scenario_MediumA_Fast_Results",
                 "Scenario_MediumE_Fast_Results",
                 "Scenario_MediumG_Fast_Results",
                 "Scenario_MediumI_Fast_Results",
                 "Scenario_MediumM_Fast_Results",
                 "Scenario_MediumQ_Fast_Results")
## process data for cost-effectiveness analysis
count_doses_by_year(results,list_process,arch,scen,filepath)
cases_per_year(results,list_process,arch,scen,filepath)
```
## Fast waning | 15 mo without catch-up campaign 
```{r}
arch = c("Medium")
scen = c("Fast")
filepath = c("15moWO")
## Load all of the vaccine strategies to be analyzed in this scenario
load("~/Transmission_dynamic_model/Output/Scenario_MediumA_Fast_Results.Rdata")
Scenario_MediumA_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumD_Fast_Results.Rdata")
Scenario_MediumD_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumF_Fast_Results.Rdata")
Scenario_MediumF_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumH_Fast_Results.Rdata")
Scenario_MediumH_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumL_Fast_Results.Rdata")
Scenario_MediumL_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_MediumP_Fast_Results.Rdata")
Scenario_MediumP_Fast_Results <- results
results = c(Scenario_MediumA_Fast_Results,
            Scenario_MediumD_Fast_Results,
            Scenario_MediumF_Fast_Results,
            Scenario_MediumH_Fast_Results,
            Scenario_MediumL_Fast_Results,
            Scenario_MediumP_Fast_Results)
list_process = c("Scenario_MediumA_Fast_Results",
                 "Scenario_MediumD_Fast_Results",
                 "Scenario_MediumF_Fast_Results",
                 "Scenario_MediumH_Fast_Results",
                 "Scenario_MediumL_Fast_Results",
                 "Scenario_MediumP_Fast_Results")
## process data for cost-effectiveness analysis
count_doses_by_year(results,list_process,arch,scen,filepath)
cases_per_year(results,list_process,arch,scen,filepath)
```


### HIGH INCIDENCE
## Slow waning | 9 mo with catch-up campaign 
```{r}
arch = c("High")
scen = c("Slow")
filepath = c("9moW")
## Load all of the vaccine strategies to be analyzed in this scenario
load("~/Transmission_dynamic_model/Output/Scenario_HighA_Slow_Results.Rdata")
Scenario_HighA_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighC_Slow_Results.Rdata")
Scenario_HighC_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighG_Slow_Results.Rdata")
Scenario_HighG_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighI_Slow_Results.Rdata")
Scenario_HighI_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighK_Slow_Results.Rdata")
Scenario_HighK_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighO_Slow_Results.Rdata")
Scenario_HighO_Slow_Results <- results
results = c(Scenario_HighA_Slow_Results,
            Scenario_HighC_Slow_Results,
            Scenario_HighG_Slow_Results,
            Scenario_HighI_Slow_Results,
            Scenario_HighK_Slow_Results,
            Scenario_HighO_Slow_Results)
list_process = c("Scenario_HighA_Slow_Results",
                 "Scenario_HighC_Slow_Results",
                 "Scenario_HighG_Slow_Results",
                 "Scenario_HighI_Slow_Results",
                 "Scenario_HighK_Slow_Results",
                 "Scenario_HighO_Slow_Results")
## process data for cost-effectiveness analysis
count_doses_by_year(results,list_process,arch,scen,filepath)
cases_per_year(results,list_process,arch,scen,filepath)
```
## Slow waning | 9 mo without catch-up campaign 
```{r}
arch = c("High")
scen = c("Slow")
filepath = c("9moWO")
## Load all of the vaccine strategies to be analyzed in this scenario
load("~/Transmission_dynamic_model/Output/Scenario_HighA_Slow_Results.Rdata")
Scenario_HighA_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighB_Slow_Results.Rdata")
Scenario_HighB_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighF_Slow_Results.Rdata")
Scenario_HighF_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighH_Slow_Results.Rdata")
Scenario_HighH_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighJ_Slow_Results.Rdata")
Scenario_HighJ_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighN_Slow_Results.Rdata")
Scenario_HighN_Slow_Results <- results
results = c(Scenario_HighA_Slow_Results,
            Scenario_HighB_Slow_Results,
            Scenario_HighF_Slow_Results,
            Scenario_HighH_Slow_Results,
            Scenario_HighJ_Slow_Results,
            Scenario_HighN_Slow_Results)
list_process = c("Scenario_HighA_Slow_Results",
                 "Scenario_HighB_Slow_Results",
                 "Scenario_HighF_Slow_Results",
                 "Scenario_HighH_Slow_Results",
                 "Scenario_HighJ_Slow_Results",
                 "Scenario_HighN_Slow_Results")
## process data for cost-effectiveness analysis
count_doses_by_year(results,list_process,arch,scen,filepath)
cases_per_year(results,list_process,arch,scen,filepath)
```
## Fast waning | 9 mo with catch-up campaign 
```{r}
arch = c("High")
scen = c("Fast")
filepath = c("9moW")
## Load all of the vaccine strategies to be analyzed in this scenario
load("~/Transmission_dynamic_model/Output/Scenario_HighA_Fast_Results.Rdata")
Scenario_HighA_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighC_Fast_Results.Rdata")
Scenario_HighC_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighG_Fast_Results.Rdata")
Scenario_HighG_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighI_Fast_Results.Rdata")
Scenario_HighI_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighK_Fast_Results.Rdata")
Scenario_HighK_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighO_Fast_Results.Rdata")
Scenario_HighO_Fast_Results <- results
results = c(Scenario_HighA_Fast_Results,
            Scenario_HighC_Fast_Results,
            Scenario_HighG_Fast_Results,
            Scenario_HighI_Fast_Results,
            Scenario_HighK_Fast_Results,
            Scenario_HighO_Fast_Results)
list_process = c("Scenario_HighA_Fast_Results",
                 "Scenario_HighC_Fast_Results",
                 "Scenario_HighG_Fast_Results",
                 "Scenario_HighI_Fast_Results",
                 "Scenario_HighK_Fast_Results",
                 "Scenario_HighO_Fast_Results")
## process data for cost-effectiveness analysis
count_doses_by_year(results,list_process,arch,scen,filepath)
cases_per_year(results,list_process,arch,scen,filepath)
```
## Fast waning | 9 mo without catch-up campaign 
```{r}
arch = c("High")
scen = c("Fast")
filepath = c("9moWO")
## Load all of the vaccine strategies to be analyzed in this scenario
load("~/Transmission_dynamic_model/Output/Scenario_HighA_Fast_Results.Rdata")
Scenario_HighA_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighB_Fast_Results.Rdata")
Scenario_HighB_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighF_Fast_Results.Rdata")
Scenario_HighF_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighH_Fast_Results.Rdata")
Scenario_HighH_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighJ_Fast_Results.Rdata")
Scenario_HighJ_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighN_Fast_Results.Rdata")
Scenario_HighN_Fast_Results <- results
results = c(Scenario_HighA_Fast_Results,
            Scenario_HighB_Fast_Results,
            Scenario_HighF_Fast_Results,
            Scenario_HighH_Fast_Results,
            Scenario_HighJ_Fast_Results,
            Scenario_HighN_Fast_Results)
list_process = c("Scenario_HighA_Fast_Results",
                 "Scenario_HighB_Fast_Results",
                 "Scenario_HighF_Fast_Results",
                 "Scenario_HighH_Fast_Results",
                 "Scenario_HighJ_Fast_Results",
                 "Scenario_HighN_Fast_Results")
## process data for cost-effectiveness analysis
count_doses_by_year(results,list_process,arch,scen,filepath)
cases_per_year(results,list_process,arch,scen,filepath)
```
## Slow waning | 15 mo with catch-up campaign 
```{r}
arch = c("High")
scen = c("Slow")
filepath = c("15moW")
## Load all of the vaccine strategies to be analyzed in this scenario
load("~/Transmission_dynamic_model/Output/Scenario_HighA_Slow_Results.Rdata")
Scenario_HighA_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighE_Slow_Results.Rdata")
Scenario_HighE_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighG_Slow_Results.Rdata")
Scenario_HighG_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighI_Slow_Results.Rdata")
Scenario_HighI_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighM_Slow_Results.Rdata")
Scenario_HighM_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighQ_Slow_Results.Rdata")
Scenario_HighQ_Slow_Results <- results
results = c(Scenario_HighA_Slow_Results,
            Scenario_HighE_Slow_Results,
            Scenario_HighG_Slow_Results,
            Scenario_HighI_Slow_Results,
            Scenario_HighM_Slow_Results,
            Scenario_HighQ_Slow_Results)
list_process = c("Scenario_HighA_Slow_Results",
                 "Scenario_HighE_Slow_Results",
                 "Scenario_HighG_Slow_Results",
                 "Scenario_HighI_Slow_Results",
                 "Scenario_HighM_Slow_Results",
                 "Scenario_HighQ_Slow_Results")
## process data for cost-effectiveness analysis
count_doses_by_year(results,list_process,arch,scen,filepath)
cases_per_year(results,list_process,arch,scen,filepath)
```
## Slow waning | 15 mo without catch-up campaign 
```{r}
arch = c("High")
scen = c("Slow")
filepath = c("15moWO")
## Load all of the vaccine strategies to be analyzed in this scenario
load("~/Transmission_dynamic_model/Output/Scenario_HighA_Slow_Results.Rdata")
Scenario_HighA_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighD_Slow_Results.Rdata")
Scenario_HighD_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighF_Slow_Results.Rdata")
Scenario_HighF_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighH_Slow_Results.Rdata")
Scenario_HighH_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighL_Slow_Results.Rdata")
Scenario_HighL_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighP_Slow_Results.Rdata")
Scenario_HighP_Slow_Results <- results
results = c(Scenario_HighA_Slow_Results,
            Scenario_HighD_Slow_Results,
            Scenario_HighF_Slow_Results,
            Scenario_HighH_Slow_Results,
            Scenario_HighL_Slow_Results,
            Scenario_HighP_Slow_Results)
list_process = c("Scenario_HighA_Slow_Results",
                 "Scenario_HighD_Slow_Results",
                 "Scenario_HighF_Slow_Results",
                 "Scenario_HighH_Slow_Results",
                 "Scenario_HighL_Slow_Results",
                 "Scenario_HighP_Slow_Results")
## process data for cost-effectiveness analysis
count_doses_by_year(results,list_process,arch,scen,filepath)
cases_per_year(results,list_process,arch,scen,filepath)
```
## Fast waning | 15 mo with catch-up campaign 
```{r}
arch = c("High")
scen = c("Fast")
filepath = c("15moW")
## Load all of the vaccine strategies to be analyzed in this scenario
load("~/Transmission_dynamic_model/Output/Scenario_HighA_Fast_Results.Rdata")
Scenario_HighA_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighE_Fast_Results.Rdata")
Scenario_HighE_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighG_Fast_Results.Rdata")
Scenario_HighG_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighI_Fast_Results.Rdata")
Scenario_HighI_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighM_Fast_Results.Rdata")
Scenario_HighM_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighQ_Fast_Results.Rdata")
Scenario_HighQ_Fast_Results <- results
results = c(Scenario_HighA_Fast_Results,
            Scenario_HighE_Fast_Results,
            Scenario_HighG_Fast_Results,
            Scenario_HighI_Fast_Results,
            Scenario_HighM_Fast_Results,
            Scenario_HighQ_Fast_Results)
list_process = c("Scenario_HighA_Fast_Results",
                 "Scenario_HighE_Fast_Results",
                 "Scenario_HighG_Fast_Results",
                 "Scenario_HighI_Fast_Results",
                 "Scenario_HighM_Fast_Results",
                 "Scenario_HighQ_Fast_Results")
## process data for cost-effectiveness analysis
count_doses_by_year(results,list_process,arch,scen,filepath)
cases_per_year(results,list_process,arch,scen,filepath)
```
## Fast waning | 15 mo without catch-up campaign 
```{r}
arch = c("High")
scen = c("Fast")
filepath = c("15moWO")
## Load all of the vaccine strategies to be analyzed in this scenario
load("~/Transmission_dynamic_model/Output/Scenario_HighA_Fast_Results.Rdata")
Scenario_HighA_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighD_Fast_Results.Rdata")
Scenario_HighD_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighF_Fast_Results.Rdata")
Scenario_HighF_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighH_Fast_Results.Rdata")
Scenario_HighH_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighL_Fast_Results.Rdata")
Scenario_HighL_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_HighP_Fast_Results.Rdata")
Scenario_HighP_Fast_Results <- results
results = c(Scenario_HighA_Fast_Results,
            Scenario_HighD_Fast_Results,
            Scenario_HighF_Fast_Results,
            Scenario_HighH_Fast_Results,
            Scenario_HighL_Fast_Results,
            Scenario_HighP_Fast_Results)
list_process = c("Scenario_HighA_Fast_Results",
                 "Scenario_HighD_Fast_Results",
                 "Scenario_HighF_Fast_Results",
                 "Scenario_HighH_Fast_Results",
                 "Scenario_HighL_Fast_Results",
                 "Scenario_HighP_Fast_Results")
## process data for cost-effectiveness analysis
count_doses_by_year(results,list_process,arch,scen,filepath)
cases_per_year(results,list_process,arch,scen,filepath)
```

### VERY HIGH INCIDENCE
## Slow waning | 9 mo with catch-up campaign 
```{r}
arch = c("VeryHigh")
scen = c("Slow")
filepath = c("9moW")
## Load all of the vaccine strategies to be analyzed in this scenario
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighA_Slow_Results.Rdata")
Scenario_VeryHighA_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighC_Slow_Results.Rdata")
Scenario_VeryHighC_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighG_Slow_Results.Rdata")
Scenario_VeryHighG_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighI_Slow_Results.Rdata")
Scenario_VeryHighI_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighK_Slow_Results.Rdata")
Scenario_VeryHighK_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighO_Slow_Results.Rdata")
Scenario_VeryHighO_Slow_Results <- results
results = c(Scenario_VeryHighA_Slow_Results,
            Scenario_VeryHighC_Slow_Results,
            Scenario_VeryHighG_Slow_Results,
            Scenario_VeryHighI_Slow_Results,
            Scenario_VeryHighK_Slow_Results,
            Scenario_VeryHighO_Slow_Results)
list_process = c("Scenario_VeryHighA_Slow_Results",
                 "Scenario_VeryHighC_Slow_Results",
                 "Scenario_VeryHighG_Slow_Results",
                 "Scenario_VeryHighI_Slow_Results",
                 "Scenario_VeryHighK_Slow_Results",
                 "Scenario_VeryHighO_Slow_Results")
## process data for cost-effectiveness analysis
count_doses_by_year(results,list_process,arch,scen,filepath)
cases_per_year(results,list_process,arch,scen,filepath)
```
## Slow waning | 9 mo without catch-up campaign 
```{r}
arch = c("VeryHigh")
scen = c("Slow")
filepath = c("9moWO")
## Load all of the vaccine strategies to be analyzed in this scenario
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighA_Slow_Results.Rdata")
Scenario_VeryHighA_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighB_Slow_Results.Rdata")
Scenario_VeryHighB_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighF_Slow_Results.Rdata")
Scenario_VeryHighF_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighH_Slow_Results.Rdata")
Scenario_VeryHighH_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighJ_Slow_Results.Rdata")
Scenario_VeryHighJ_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighN_Slow_Results.Rdata")
Scenario_VeryHighN_Slow_Results <- results
results = c(Scenario_VeryHighA_Slow_Results,
            Scenario_VeryHighB_Slow_Results,
            Scenario_VeryHighF_Slow_Results,
            Scenario_VeryHighH_Slow_Results,
            Scenario_VeryHighJ_Slow_Results,
            Scenario_VeryHighN_Slow_Results)
list_process = c("Scenario_VeryHighA_Slow_Results",
                 "Scenario_VeryHighB_Slow_Results",
                 "Scenario_VeryHighF_Slow_Results",
                 "Scenario_VeryHighH_Slow_Results",
                 "Scenario_VeryHighJ_Slow_Results",
                 "Scenario_VeryHighN_Slow_Results")
## process data for cost-effectiveness analysis
count_doses_by_year(results,list_process,arch,scen,filepath)
cases_per_year(results,list_process,arch,scen,filepath)
```
## Fast waning | 9 mo with catch-up campaign 
```{r}
arch = c("VeryHigh")
scen = c("Fast")
filepath = c("9moW")
## Load all of the vaccine strategies to be analyzed in this scenario
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighA_Fast_Results.Rdata")
Scenario_VeryHighA_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighC_Fast_Results.Rdata")
Scenario_VeryHighC_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighG_Fast_Results.Rdata")
Scenario_VeryHighG_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighI_Fast_Results.Rdata")
Scenario_VeryHighI_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighK_Fast_Results.Rdata")
Scenario_VeryHighK_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighO_Fast_Results.Rdata")
Scenario_VeryHighO_Fast_Results <- results
results = c(Scenario_VeryHighA_Fast_Results,
            Scenario_VeryHighC_Fast_Results,
            Scenario_VeryHighG_Fast_Results,
            Scenario_VeryHighI_Fast_Results,
            Scenario_VeryHighK_Fast_Results,
            Scenario_VeryHighO_Fast_Results)
list_process = c("Scenario_VeryHighA_Fast_Results",
                 "Scenario_VeryHighC_Fast_Results",
                 "Scenario_VeryHighG_Fast_Results",
                 "Scenario_VeryHighI_Fast_Results",
                 "Scenario_VeryHighK_Fast_Results",
                 "Scenario_VeryHighO_Fast_Results")
## process data for cost-effectiveness analysis
count_doses_by_year(results,list_process,arch,scen,filepath)
cases_per_year(results,list_process,arch,scen,filepath)
```
## Fast waning | 9 mo without catch-up campaign 
```{r}
arch = c("VeryHigh")
scen = c("Fast")
filepath = c("9moWO")
## Load all of the vaccine strategies to be analyzed in this scenario
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighA_Fast_Results.Rdata")
Scenario_VeryHighA_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighB_Fast_Results.Rdata")
Scenario_VeryHighB_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighF_Fast_Results.Rdata")
Scenario_VeryHighF_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighH_Fast_Results.Rdata")
Scenario_VeryHighH_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighJ_Fast_Results.Rdata")
Scenario_VeryHighJ_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighN_Fast_Results.Rdata")
Scenario_VeryHighN_Fast_Results <- results
results = c(Scenario_VeryHighA_Fast_Results,
            Scenario_VeryHighB_Fast_Results,
            Scenario_VeryHighF_Fast_Results,
            Scenario_VeryHighH_Fast_Results,
            Scenario_VeryHighJ_Fast_Results,
            Scenario_VeryHighN_Fast_Results)
list_process = c("Scenario_VeryHighA_Fast_Results",
                 "Scenario_VeryHighB_Fast_Results",
                 "Scenario_VeryHighF_Fast_Results",
                 "Scenario_VeryHighH_Fast_Results",
                 "Scenario_VeryHighJ_Fast_Results",
                 "Scenario_VeryHighN_Fast_Results")
## process data for cost-effectiveness analysis
count_doses_by_year(results,list_process,arch,scen,filepath)
cases_per_year(results,list_process,arch,scen,filepath)
```
## Slow waning | 15 mo with catch-up campaign 
```{r}
arch = c("VeryHigh")
scen = c("Slow")
filepath = c("15moW")
## Load all of the vaccine strategies to be analyzed in this scenario
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighA_Slow_Results.Rdata")
Scenario_VeryHighA_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighE_Slow_Results.Rdata")
Scenario_VeryHighE_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighG_Slow_Results.Rdata")
Scenario_VeryHighG_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighI_Slow_Results.Rdata")
Scenario_VeryHighI_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighM_Slow_Results.Rdata")
Scenario_VeryHighM_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighQ_Slow_Results.Rdata")
Scenario_VeryHighQ_Slow_Results <- results
results = c(Scenario_VeryHighA_Slow_Results,
            Scenario_VeryHighE_Slow_Results,
            Scenario_VeryHighG_Slow_Results,
            Scenario_VeryHighI_Slow_Results,
            Scenario_VeryHighM_Slow_Results,
            Scenario_VeryHighQ_Slow_Results)
list_process = c("Scenario_VeryHighA_Slow_Results",
                 "Scenario_VeryHighE_Slow_Results",
                 "Scenario_VeryHighG_Slow_Results",
                 "Scenario_VeryHighI_Slow_Results",
                 "Scenario_VeryHighM_Slow_Results",
                 "Scenario_VeryHighQ_Slow_Results")
## process data for cost-effectiveness analysis
count_doses_by_year(results,list_process,arch,scen,filepath)
cases_per_year(results,list_process,arch,scen,filepath)
```
## Slow waning | 15 mo without catch-up campaign 
```{r}
arch = c("VeryHigh")
scen = c("Slow")
filepath = c("15moWO")
## Load all of the vaccine strategies to be analyzed in this scenario
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighA_Slow_Results.Rdata")
Scenario_VeryHighA_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighD_Slow_Results.Rdata")
Scenario_VeryHighD_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighF_Slow_Results.Rdata")
Scenario_VeryHighF_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighH_Slow_Results.Rdata")
Scenario_VeryHighH_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighL_Slow_Results.Rdata")
Scenario_VeryHighL_Slow_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighP_Slow_Results.Rdata")
Scenario_VeryHighP_Slow_Results <- results
results = c(Scenario_VeryHighA_Slow_Results,
            Scenario_VeryHighD_Slow_Results,
            Scenario_VeryHighF_Slow_Results,
            Scenario_VeryHighH_Slow_Results,
            Scenario_VeryHighL_Slow_Results,
            Scenario_VeryHighP_Slow_Results)
list_process = c("Scenario_VeryHighA_Slow_Results",
                 "Scenario_VeryHighD_Slow_Results",
                 "Scenario_VeryHighF_Slow_Results",
                 "Scenario_VeryHighH_Slow_Results",
                 "Scenario_VeryHighL_Slow_Results",
                 "Scenario_VeryHighP_Slow_Results")
## process data for cost-effectiveness analysis
count_doses_by_year(results,list_process,arch,scen,filepath)
cases_per_year(results,list_process,arch,scen,filepath)
```
## Fast waning | 15 mo with catch-up campaign 
```{r}
arch = c("VeryHigh")
scen = c("Fast")
filepath = c("15moW")
## Load all of the vaccine strategies to be analyzed in this scenario
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighA_Fast_Results.Rdata")
Scenario_VeryHighA_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighE_Fast_Results.Rdata")
Scenario_VeryHighE_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighG_Fast_Results.Rdata")
Scenario_VeryHighG_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighI_Fast_Results.Rdata")
Scenario_VeryHighI_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighM_Fast_Results.Rdata")
Scenario_VeryHighM_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighQ_Fast_Results.Rdata")
Scenario_VeryHighQ_Fast_Results <- results
results = c(Scenario_VeryHighA_Fast_Results,
            Scenario_VeryHighE_Fast_Results,
            Scenario_VeryHighG_Fast_Results,
            Scenario_VeryHighI_Fast_Results,
            Scenario_VeryHighM_Fast_Results,
            Scenario_VeryHighQ_Fast_Results)
list_process = c("Scenario_VeryHighA_Fast_Results",
                 "Scenario_VeryHighE_Fast_Results",
                 "Scenario_VeryHighG_Fast_Results",
                 "Scenario_VeryHighI_Fast_Results",
                 "Scenario_VeryHighM_Fast_Results",
                 "Scenario_VeryHighQ_Fast_Results")
## process data for cost-effectiveness analysis
count_doses_by_year(results,list_process,arch,scen,filepath)
cases_per_year(results,list_process,arch,scen,filepath)
```
## Fast waning | 15 mo without catch-up campaign 
```{r}
arch = c("VeryHigh")
scen = c("Fast")
filepath = c("15moWO")
## Load all of the vaccine strategies to be analyzed in this scenario
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighA_Fast_Results.Rdata")
Scenario_VeryHighA_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighD_Fast_Results.Rdata")
Scenario_VeryHighD_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighF_Fast_Results.Rdata")
Scenario_VeryHighF_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighH_Fast_Results.Rdata")
Scenario_VeryHighH_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighL_Fast_Results.Rdata")
Scenario_VeryHighL_Fast_Results <- results
load("~/Transmission_dynamic_model/Output/Scenario_VeryHighP_Fast_Results.Rdata")
Scenario_VeryHighP_Fast_Results <- results
results = c(Scenario_VeryHighA_Fast_Results,
            Scenario_VeryHighD_Fast_Results,
            Scenario_VeryHighF_Fast_Results,
            Scenario_VeryHighH_Fast_Results,
            Scenario_VeryHighL_Fast_Results,
            Scenario_VeryHighP_Fast_Results)
list_process = c("Scenario_VeryHighA_Fast_Results",
                 "Scenario_VeryHighD_Fast_Results",
                 "Scenario_VeryHighF_Fast_Results",
                 "Scenario_VeryHighH_Fast_Results",
                 "Scenario_VeryHighL_Fast_Results",
                 "Scenario_VeryHighP_Fast_Results")
## process data for cost-effectiveness analysis
count_doses_by_year(results,list_process,arch,scen,filepath)
cases_per_year(results,list_process,arch,scen,filepath)
```


